Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
approach again

\section{Introduction}

@@

\section{Approach}

\frame{
\frametitle{What }
\begin{itemize}
	\item
\end{itemize}
}

\frame{
\frametitle{Our Approach}
\begin{itemize}
	\item Hierarchical Architecture
	\begin{itemize}
		\item Controllers' view do not span the whole network, but only the 'underlying network'
		\item Each controller behaves as a giant openflow switch for parent controller (Network Aggregation)
		\item Controller translates OFP commands and network updates between parent controller and underlying networks
	\end{itemize}
	\item Network Aggregation
	\begin{itemize}
		\item Share a condensed view of the network: A Network flow table
		\item Surpress network events such that aggregated network does not change: Reduce communication overhead
		\item Convert flow addtion/removal commands on aggregated network to actual network in an efficient way
	\end{itemize}
	\item Timestamp: 
		\item Handle domain level inconsistencies in "SDN Datapath" (Domain Network)
		\item Each domain i maintains a vector timestamp T_i[1...n] 
		\item (Routers in) A Domain may change flow depending on their timestamps
	\end{itemize}   
\end{itemize}
}

\section{Progress}

\frame{
\frametitle{Network Aggregation}
\begin{itemize}
	\item
\end{itemize}
}

\frame{
\frametitle{Timestamp}
\begin{itemize}
	\item
\end{itemize}
}

>>>>

\section{Introduction and Related Work}

@@

\section{Approach and Progress}

\frame{
\frametitle{Our Approach}
\begin{itemize}
\item What is being done ? 
	\begin{itemize}
		\item It's a Replicated state machine (strong or lazy replication) architecture, which had been well studied in Distributed Systems community
		\item Past work uses DHTs (Onix), Transactional DB (Onix), DFS (Hyperflow)
	\end{itemize}
	\item We are trying to study		
	\begin{itemize}
		\item Instead of using a general repilication mechanism, can we exploit the fact that network views are being replicated ?
		\item Could the SDN datapath (replication client) make use of replication timestamps ?
	\end{itemize}

\end{itemize}
}

\frame{
\frametitle{Hierarchical Architecture}
\begin{itemize}
	\item Hierarchical Architecture
	\begin{itemize}
		\item Controllers' view do not span the whole network, but only the 'underlying network'
		\item Each controller behaves as a giant openflow switch for parent controller (Network Aggregation)
		\item Controller translates OFP commands and network updates between parent controller and underlying networks
	\end{itemize}
\end{itemize}
}

\frame{
\frametitle{Network Aggregation}
	\begin{itemize}
		\item Share a condensed view of the network: A Network flow table
		\item Surpress network events such that aggregated network does not change: Reduce communication overhead
		\item Convert flow addtion/removal commands on aggregated network to actual network in an efficient way

	\end{itemize}
}

\frame{
\frametitle{Timestamp}
	\begin{itemize}   
		\item Handle domain level inconsistencies in Domain Network
		\item Each domain i maintains a vector timestamp, conistsing of revision number of domains
		\item Border routers in a domain may change a flow depending on it's timestamp
	\end{itemize}   
}
